Mental Health Plays Significant Role in Physical Wellness From 1972 to 2022 US General Social Surveys

### 2024-04-23 paper/paper.qmd
Fix typo and code styling

Based on @tbl-modelresults, however, although having influences on linear equation in @fig-mental-vs-physical, depression diagnosis's influences on counted days of feeling physically unwell is not significant ($\beta_2$ = −1.43, p = .22). Counted days of feeling mentally unwell, on the other hand, do have a significant positive correlation with counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01). From @fig-mental-vs-physical, it is evident to state that depression diagnosis may be a moderator to strengthen the relationship between counted ays of mental and physical unwellness in the past 30 days. The lack of significance could be due to possible errors, validity of survey questions, biases, or other possible factors. Hence, even though one of the correlations is not significant, it is still important for us to consider the variable for possible future research.

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```
\break
### Diagnostics

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

Based on @tbl-modelresults, however, although having influences on linear equation in @fig-mental-vs-physical, depression diagnosis's influences on counted days of feeling physically unwell is not significant ($\beta_2$ = 1.44, p = .22). Counted days of feeling mentally unwell, on the other hand, do have a significant positive correlation with counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01). From @fig-mental-vs-physical, it is evident to state that depression diagnosis may be a moderator to strengthen the relationship between counted ays of mental and physical unwellness in the past 30 days. The lack of significance could be due to possible errors, validity of survey questions, biases, or other possible factors. Hence, even though one of the correlations is not significant, it is still important for us to consider the variable for possible future research.

@@

model <-
  readRDS(file = here::here("models/model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "Model" = model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

pp_check(model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```
\break
### Diagnostics

@@

plot(model, "trace")

plot(model, "rhat")
```
